
---
title: "Check"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-04-30"
output: 
  word_document:
    reference_docx: ../../common/word_reference_style.docx
---


```{r set-options, echo=FALSE, cache=FALSE, warning=FALSE, results='hide'}
rm(list=ls())
options(width = 200)
show_code = FALSE
source("lib/functions.R")
source("lib/get_data.R")
source("lib/generate_data_frames.R")
source("lib/standardisation.R")
```
#Methods

```{r data_preparation, echo=FALSE, cache=FALSE, results="hide", warning=FALSE}

data.cache( generate_data_frames, frequency='yearly')


read.dta13('/mnt/sda5/store/aarnet_owncloud/Sharing_between_mofi_and_dennis/Opioid/Opioid/Continuing users for Dennis to check.dta') %>% 
  as.tibble() %>% 
  { . } -> df_mofi
#
df_mofi %>%
  select(-lga) %>%
  rename( lga=lgacode,
         pin=ID, 
         sex=sex2,
         quantity=qty,
         quarter=dup,
         supply_date=DateSupply,
         unit_wt = Unit_wt,
         ddd_mg_factor = DDD,
         item_code = Item_code ,
         n_dose = DDD_q,
         )  %>%
  mutate( state=str_trim( state ),
         sex = substring( sex,1,1),
         age = age_grouping_mofi( age),
         lga = as.character( lga ) ,
         item_code = str_trim(item_code ), 
         supply_year=as.factor(substring( supply_date,6,9 )),
         usage_category = levels(df_patient_usage$usage_category)[ userType4 ] ,
         )  %>% 
  filter( !is.na( quantity )) %>% 
  { . } -> df_mofi

 

```
```{r fixup_data}

#
#df_mofi %>% 
#  filter( item_code != '91194Q') %>% 
#  { . } -> df_mofi
#
#df_mofi %>% 
#  filter( !is.na(lga )) %>% 
#  { . } -> df_mofi
#
#df_mofi %>% 
# filter( state!='ACT') %>% 
#  { . } -> df_mofi

df %>% 
  filter( !endsWith(lga, '_NA' )) %>% 
  { . } -> df

df %>% 
  distinct (pin, sex, age, state, lga) %>% 
  mutate( sex = as.factor(sex)) %>%
  inner_join( df_patient_scheme, by="pin") %>%
  {.} -> df_patient

df%>%  
  group_by(pin,  supply_year) %>%
  summarise(
            n_dose = sum(n_dose),
            quantity = sum(quantity),
            n_script = n()
            ) %>%
  ungroup() %>%
  {.} -> df_patient_dose

#
df%>%
  group_by(pin) %>%
  summarise( 
            n_quarter = n_distinct( quarter ),
            usage_category= cut( n_quarter, 
                                c(-1, 1,6,11, 18), 
                                labels = qw("one-off medium-episodic long-episodic chronic")),
            ordered_result=TRUE
            ) %>%
  {.} -> df_patient_usage

```

```{r}


bothDiff( 
         df_mofi %>% count( item_code  ),
         df %>% count( item_code  ) ,
         by='item_code')

bothDiff( 
         df_mofi %>% count( item_code  ),
         df %>% count( item_code  ) 
         )


bothDiff( 
         df_mofi %>% count( pin  ),
         df %>% count( pin  ) ,
         )

bothDiff( 
         df_mofi %>% count( pin  ),
         df %>% count( pin  ) ,
         by='pin'
         )


bothDiff( 
         df_mofi %>% count( lga  ),
         df %>% count( lga  ) ,
         by='lga'
         )

bothDiff( 
         df_mofi %>% count( lga  ),
         df %>% count( lga  ) ,
         )



bothDiff( 
         df_mofi %>% count( n_dose  ),
          df %>% count( n_dose  ) ,
         )


bothDiff( 
         df_mofi %>%
           select( item_code, unit_wt ) %>%
           distinct( item_code, unit_wt ), 
         df %>% 
           select( item_code, unit_wt ) %>%
           distinct( item_code, unit_wt ), 
         by='item_code'
)

bothDiff( 
df_mofi %>%
  select( item_code, unit_wt ) %>%
  distinct( item_code, unit_wt ), 
df %>% 
  select( item_code, unit_wt ) %>%
  distinct( item_code, unit_wt ), 
)

df_mofi %>%
  select( item_code, unit_wt ) %>%
  distinct( item_code, unit_wt ) %>% summarise( sum( unit_wt ))

df %>% 
  select( item_code, unit_wt ) %>%
  distinct( item_code, unit_wt ) %>% summarise( sum( unit_wt ))


bothDiff(
df_mofi %>% distinct( pin, usage_category ),
df_patient_usage
)

df_mofi %>% filter( pin=='7920815992') %>% distinct(eventdate)
df_mofi %>% filter( pin=='7920815992') %>% distinct(supply_date, eventdate, quarter) %>% arrange( desc( eventdate)) %>% View
df_mofi %>% filter( pin=='7920815992') %>% distinct(quarter) %>% arrange( desc(quarter)) %>% View

df_mofi %>% summarise( max( quarter))

df %>% filter( pin=='7920815992') %>% distinct(supply_date)
df %>% filter( pin=='7920815992') %>% distinct(quarter)

df_mofi %>% 
  select( pin, starts_with('Q'), -quantity, -quarter) %>%
  gather( quarter, is, -pin ) %>%
  filter( is==1 ) %>%
  distinct() %>%
  count(pin) %>% 
  { . } -> df_mofi_quarters

df_mofi_quarters %>% filter( pin=='7920815992') 

summarise( df_mofi, sum(n_dose, na.rm=TRUE ))
summarise( df, sum(n_dose, na.rm=TRUE ))



bothDiff( 
         df_mofi %>%
           group_by( item_code ) %>%
           summarise( n_dose = sum( n_dose )) ,
         df %>% 
           group_by( item_code ) %>%
           summarise( n_dose = sum( n_dose )) ,
         )

bothDiff(
         distinct( df_mofi, item_code ), 
         distinct( df, item_code )
         )


bothDiff(
         distinct( df_mofi, pin ), 
         distinct( df, pin )
         )


bothDiff(
         distinct( df_mofi, n_dose ), 
        distinct( df, n_dose )
         )

sum( df_mofi$n_dose )
sum( df$n_dose )

```

```{r standardisation}

df_patient_usage %>%
  inner_join( df_patient ) %>%
  inner_join( df_patient_dose ) %>%
  select_and_standardise_ddd ( qw('usage_category supply_year lga'), join_with=qw('supply_year') ) %>%
  print()


df_mofi %>%
  group_by( supply_year, lga, userType4 
  summarise( 
  select_and_standardise_ddd ( qw('usage_category supply_year lga'), join_with=qw('supply_year') ) %>%

   inner_join( mofi_ddd ) %>%
  mutate( dddm = dddm*10) %>%
  filter( abs( ddd - dddm) > .01 ) %>%
  arrange( desc( abs( ddd - dddm) )) %>%
  count( usage_category )



```{r see_if_mofi_gets_th_same_as_me_quartiles}



df_patient_usage %>%
  inner_join( df_patient ) %>%
  inner_join( df_patient_dose ) %>%
  select_and_standardise_ddd ( qw('usage_category supply_year lga'), join_with=qw('supply_year') ) %>%
  group_by( usage_category, supply_year ) %>%
  mutate( quartile = cut( ddd, quantile( ddd, type=2 ), labels=1:4)) %>%
  ungroup() %>%
  filter( usage_category=='chronic' & quartile==4) %>%
  count( lga ) %>%
  count(n)

df_mofi %>%
  select_and_standardise_ddd ( qw('userType4 supply_year lga'), join_with=qw('supply_year') ) %>%
  group_by( userType4, supply_year ) %>%
  mutate( quartile = cut( ddd, quantile( ddd, type=2 ), labels=1:4)) %>%
  ungroup() %>%
  filter( userType4==4 & quartile==4) %>%
  count( lga ) %>%
  count(n)


bothDiff(   
  df_mofi %>%
    distinct( userType4, pin ) %>%
    mutate( usage_category = levels(df_patient_usage$usage_category)[ userType4 ] ) %>%
    select( pin, usage_category ), 
  df_patient_usage %>%
    select( pin, usage_category ), 
  by='pin'
)


df_mofi %>%
  select( DDD_q_sayl, supply_year, lga, sex, age, usage_category ) %>%
  distinct() %>% 
  { . } -> a

df_patient_usage %>%
  inner_join( df_patient ) %>%
  inner_join( df_patient_dose ) %>%
  ungroup() %>%
  group_by(  supply_year, lga, sex, age, usage_category ) %>% 
  summarise( n_dose = sum( n_dose )) %>%
  { . } -> b

sum(b$n_dose)
sum(a$DDD_q_sayl)

bothDiff( a, b )

df %>%
  inner_join( df_patient_usage) %>%
  filter( usage_category == 'long-episodic' &
         age=='65+' &
         sex=='M' &
         lga == '18710' &
         supply_year=='2016' ) %>%
  select( n_dose, everything())
 
df_mofi %>%
  filter( usage_category == 'long-episodic' &
          age=='65+' &
          sex=='Male' &
          lga == '18710' &
          supply_year=='2016' ) %>%
  select( n_dose, everything()) %>% summarise( sum( n_dose ))


a %>%
  inner_join( b, by=qw("supply_year lga sex age usage_category")) %>%
  mutate( diff =  DDD_q_sayl - n_dose ) %>%
  select(  diff,  DDD_q_sayl , n_dose, everything() ) %>%
  filter( diff> .001 ) %>%
  arrange( desc( diff ))


df_mofi %>% count( Tot_NiRi )
df_mofi %>% count( NiRi )
df_mofi %>% count( pick_DDD_q_sayl )
df_mofi %>% count( AusPop )
df_mofi %>% count( AusPop, age, sex )
df_mofi %>% count( AusPop, supply_year, state)
df_mofi %>% count( populato)
df_mofi %>% count(  supply_year, age, sex,lga)
df_mofi %>% count( pick_DDD_q_sayl )
df_mofi %>% count( lga )
df_mofi %>% count( xxx )

232*2*4

df %>% distinct( pin, lga ) %>% count( lga )

df_mofi %>% select( )

  select_and_standardise_ddd ( qw('usage_category supply_year lga'), join_with=qw('supply_year') ) %>%
    print()

df_population %>%
  group_by( supply_year ) %>%
  summarise( sum( population ))

# part 1 

df_mofi %>% 
  filter( pick_DDD_q_sayl == 1 ) %>%
  select(  qw('usage_category supply_year lga age sex DDD_q_sayl ') ) %>% 
  { . } -> a

df %>%
  inner_join( df_patient_usage) %>%
  group_by(usage_category,supply_year,lga,age,sex) %>%
  dplyr::summarise( n_dose = sum( n_dose ) ) %>%
  ungroup() %>% 
  { . } -> b

bothDiff(a,b)

inner_join( a,b) 

sum(a$DDD_q_sayl)
sum(b$n_dose)
# we have the same n_dose / DDD_q_sayl

# part2

df_mofi %>% 
  filter( pick_DDD_q_sayl == 1 ) %>%
  select(  qw('usage_category supply_year lga age sex DDD_q_sayl populato ') ) %>% 
  { . } -> a

df %>%
  inner_join( df_patient_usage) %>%
  group_by(usage_category,supply_year,lga,age,sex) %>%
  dplyr::summarise( n_dose = sum( n_dose ) ) %>%
  ungroup() %>% 
  f_join_population( qw('usage_category supply_year lga age sex ') ) %>% 
  { . } -> b

bothDiff(a,b)

inner_join( a,b) 

sum(a$populato)
sum(b$population)
# we have the same population by lga, supply_year, age, sex

# part3

df_mofi %>% 
  filter( pick_DDD_q_sayl == 1 ) %>%
  select(  qw('usage_category supply_year lga age sex DDD_q_sayl populato AusPop NiRi Tot_NiRi') ) %>% 
  mutate( m_niri =(DDD_q_sayl/populato)*AusPop ) %>%
  group_by(usage_category,supply_year,lga, Tot_NiRi) %>%
  summarise( m_totniri = sum( NiRi )) %>%
  { . } -> a

df %>%
  inner_join( df_patient_usage) %>%
  group_by(usage_category,supply_year,lga,age,sex) %>%
  dplyr::summarise( n_dose = sum( n_dose ) ) %>%
  ungroup() %>% 
  f_join_population( qw('usage_category supply_year lga age sex ') ) %>% 
  group_by(usage_category,lga,age,sex) %>%
  dplyr::summarise( proportion = sum((n_dose * 1000 * 10)) / sum(population * my_year_length( supply_year ) )) %>%  # calculate proportion at this level
  { . } -> b

bothDiff(a,b)

inner_join( a,b) 

sum(a$populato)
sum(b$population)


# egen DDD_q_sayl=sum(DDD_q), by (year lgacode sex2 age4 userType4)
# egen pick_DDD_q_sayl=tag (DDD_q_sayl year lgacode sex2 age4 userType4)
# ge NiRi=(DDD_q_sayl/populato)*AusPop if pick_DDD_q_sayl==1
# egen Tot_NiRi=sum(NiRi), by (year lgacode userType4)
# ge xxx=.
# replace xxx=(Tot_NiRi*1000)/(24210809*365) if year==2013
# replace xxx=(Tot_NiRi*1000)/(24210809*365) if year==2014
# replace xxx=(Tot_NiRi*1000)/(24210809*365) if year==2015
# replace xxx=(Tot_NiRi*1000)/(24210809*366) if year==2016
#  
# egen pick_xxx= tag (xxx year lgacode userType4)
# list lgacode xxx if pick_xxx==1 & year==2013 & userType4==1, noobs clean
# list lgacode xxx if pick_xxx==1 & year==2013 & userType4==2, noobs clean
# list lgacode xxx if pick_xxx==1 & year==2013 & userType4==3, noobs clean
# list lgacode xxx if pick_xxx==1 & year==2013 & userType4==4, noobs clean
