
---
title: "Check"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-04-30"
output: 
  word_document:
    reference_docx: ../../common/word_reference_style.docx
---


```{r set-options, echo=FALSE, cache=FALSE, warning=FALSE, results='hide'}
rm(list=ls())
options(width = 200)
show_code = FALSE
source("lib/functions.R")
source("lib/get_data.R")
source("lib/generate_data_frames.R")
source("lib/standardisation.R")
```
#Methods

```{r data_preparation, echo=FALSE, cache=FALSE, results="hide", warning=FALSE}

data.cache( generate_data_frames, frequency='yearly')

```
#powerpoint slide 1
```{r ppt_1, echo=FALSE}


df %<>% filter( lga != '.')

#readstata13::read.dta13( 'check/vic_nsw_newVSint.dta') -> mofi

readstata13::read.dta13( '/store/aarnet_owncloud/Sharing_between_mofi_and_dennis/please check 5 Oct 18.dta') %>%
  as.tibble() %>% 
  { . } -> mofi

mofi %>%
  rename( lga=lga,
         pin=ID, 
         sex=sex2,
         quantity=qty,
         quarter=dup,
         supply_date=DateSupply,
         unit_wt = Unit_wt,
         ddd_mg_factor = DDD,
		 item_code = Item_code 
         )  %>%
  mutate( state=str_trim( state ),
        age = age_grouping_mofi( age),
        lga = as.character( lga ) ,
		item_code = str_trim(item_code ), 
#        unit_wt=ifelse( item_code=='02124T', 2000, unit_wt),
#		ddd_mg_factor=ifelse( item_code=='08423H', 4, ddd_mg_factor),
        n_dose=quantity * unit_wt / ddd_mg_factor ,
        supply_year=as.factor(substring( supply_date,6,9 ))
        )  %>%
  filter( lga != '89399' & 
         state!='ACT' & 
#         item_code != '91194Q' &
         !is.na( pin) ) %>% 
  { . } -> mofi

#mofi %<>% filter( !is.na( pin) )

names(df) %>% setdiff( names( mofi ))

names(mofi) %>% setdiff( names( df ))

mofi %>% 
	filter( item_code == "08423H" ) %>% 
	select( item_code, GenerName, from_strenth, genricType, Item_type, ddd_mg_factor) %>% 
	distinct( )                 



read.csv( '/tmp/mozilla_dewoller0/file.csv', stringsAsFactors=FALSE) %>% as.tibble() %>%
  select( LGA, starts_with('DDD')) %>%
  gather( code, dddm, -LGA ) %>%
  separate( code, c('c1','c2'), '\\.' ) %>%
  mutate( c3 =ifelse( is.na(c2), '0', c2 ),
         c4=as.numeric( c3),
         supply_year = as.character( 2013 + floor( c4 / 4 )),
         usage_category = levels( df_patient_usage $ usage_category )[ c4 %% 4 +1 ],
         lga = as.character( LGA),
         dddm=as.numeric( dddm ))  %>%
  select( lga, supply_year, usage_category, dddm ) %>%
  filter( !is.na( dddm)) %>%
  { . } -> mofi_ddd


mofi_ddd %>% count( supply_year ) 


df_patient_usage %>%
  inner_join( df_patient ) %>%
  inner_join( df_patient_dose ) %>%
  select_and_standardise_ddd ( qw('usage_category supply_year lga'), join_with=qw('supply_year') ) %>%
  inner_join( mofi_ddd ) %>%
  mutate( dddm = dddm*10) %>%
  filter( abs( ddd - dddm) > .01 ) %>%
  arrange( desc( abs( ddd - dddm) )) %>%
  count( usage_category )

df_patient_usage %>%
  inner_join( df_patient ) %>%
  inner_join( df_patient_dose ) %>%
  select_and_standardise_ddd ( qw('usage_category supply_year lga'), join_with=qw('supply_year') ) %>%
  group_by( usage_category, supply_year ) %>%
  mutate( quartile = cut( ddd, quantile( ddd, type=2 ), labels=1:4)) %>%
  arrange( supply_year, usage_category, lga ) %>% 
  write.csv( '/tmp/continuing_ddd_adjusted.csv', row.names=FALSE)


df_patient_usage %>%
  inner_join( df_patient ) %>%
  inner_join( df_patient_dose ) %>%
  select_and_standardise_ddd ( qw('usage_category supply_year lga'), join_with=qw('supply_year') ) %>%
  group_by( usage_category, supply_year ) %>%
  mutate( quartile = cut( ddd, quantile( ddd, type=2 ), labels=1:4)) %>%
  inner_join( mofi_ddd  %>% 
             mutate( dddm = dddm*10) %>%
             group_by( usage_category, supply_year ) %>%
             mutate( quartilem = cut( dddm, quantile( dddm, type=2 ), labels=1:4)),
           by=qw('usage_category supply_year lga')) %>% 
  ungroup() %>%
           { . } -> combo_quartile

combo_quartile %>%
  filter( usage_category == 'chronic' & quartilem==4 ) %>%
  count( lga, sort=TRUE ) %>%
  count( n ) 

combo_quartile %>%
  filter( usage_category == 'chronic' & quartile==4 ) %>%
  count( lga, sort=TRUE ) %>%
  count( n ) 

mofi_ddd  %>% 
      group_by( usage_category, supply_year ) %>%
      mutate( quartilem = cut( dddm, quantile( dddm, type=2 ), labels=1:4)) %>%
      ungroup() %>%
    filter( usage_category == 'chronic' & quartilem==4 ) %>%
      count( lga, sort=TRUE ) %>%
      count( n ) 


df_patient_usage %>%
  inner_join( df_patient ) %>%
  inner_join( df_patient_dose ) %>%
  select_and_standardise_ddd ( qw('usage_category supply_year lga'), join_with=qw('supply_year') ) %>%
  group_by( usage_category, supply_year ) %>%
  mutate( quartile = cut( ddd, quantile( ddd, type=2 ), labels=1:4)) %>%
  ungroup() %>%
  filter( usage_category == 'chronic' & quartile==4 ) %>%
  count( lga, sort=TRUE ) %>%
  count( n ) 


mofi_ddd  %>% 
  group_by(  lga, supply_year ) %>%
  summarise( dddm = sum(dddm)) %>%
  group_by( supply_year ) %>%
  mutate( quartilem = cut( dddm, quantile( dddm, type=2 ), labels=1:4)) %>%
  ungroup() %>%
  filter( quartilem==4 ) %>%
  count( lga, sort=TRUE ) %>%
  count( n ) 


df_patient_usage %>%
  inner_join( df_patient ) %>%
  inner_join( df_patient_dose ) %>%
  select_and_standardise_ddd ( qw('usage_category supply_year lga'), join_with=qw('supply_year') ) %>%
  group_by(  lga, supply_year ) %>%
  summarise( ddd = sum(ddd)) %>%
  group_by( supply_year ) %>%
  mutate( quartile = cut( ddd, quantile( ddd, type=2 ), labels=1:4)) %>%
  ungroup() %>%
  filter( quartile==4 ) %>%
  count( lga, sort=TRUE ) %>%
  count( n ) 

combo_quartile %>%
  count( quartile )

  filter( quartile != quartilem ) %>%
  arrange( desc( abs( ddd - dddm) )) %>%
  count( usage_category )

# check without standardisation

df_patient_usage %>%
  inner_join( df_patient ) %>%
  inner_join( df_patient_dose ) %>%
  group_by( usage_category, supply_year, lga ) %>%
  summarise( n_dose = sum( n_dose )) %>%
  inner_join( df_population %>% 
             group_by( supply_year, lga ) %>% 
             summarise( people_days = sum( population  * my_year_length( supply_year ))),
                       by=c('supply_year', 'lga')) %>%
  mutate( ddd = n_dose * 1000*10 / people_days ) 


mofi %>% 
  filter( lgacode==10050) %>%
  select ( starts_with('DDD') )


readstata13::read.dta13( '/tmp/LGAlevel DDD in long form User this one for regression.dta')  %>%
  as.tibble() %>%
  mutate( lga=as.character( LGA ), 
         supply_year = as.character( year ) ) %>%
  select( lga, starts_with( 'UserType'), supply_year ) %>%
  gather( ut, dddm, -lga, -supply_year ) %>%
  mutate( ut = as.numeric( substring( ut, 9,9) ),
         usage_category = levels( df_patient_usage $ usage_category )[ ut ] ) %>% 
  { . } -> mofi_m2


df_patient_usage %>%
  inner_join( df_patient ) %>%
  inner_join( df_patient_dose ) %>%
  select_and_standardise_ddd ( qw('usage_category supply_year lga'), join_with=qw('supply_year') ) %>%
  inner_join( mofi_m2 ) %>%
  filter( abs( ddd - dddm) > .1 ) %>%
  arrange( desc( abs( ddd - dddm) )) %>%
  count( usage_category )



# detailed check

mofi %>% summarise( sum(DDD_t, na.rm=TRUE))
mofi %>% summarise( sum(DDD_ID, na.rm=TRUE))
mofi %>% summarise( sum(DDD_ID_Q, na.rm=TRUE))

mofi %>% distinct( Unit)
mofi %>% distinct( unit_wt)
mofi %>% distinct( item_code)
mofi %>% distinct( Item_type)
mofi %>% distinct( genricType)

mofi %>% distinct ( item_code, unit_wt, ddd_mg_factor )   -> a
df %>% distinct ( item_code, unit_wt, ddd_mg_factor )  -> b
a %>% inner_join( b , by='item_code' ) -> c

c %>%  mutate( diff = (ddd_mg_factor.x - ddd_mg_factor.y), adiff=abs(diff)  ) %>%
	filter( adiff>.1) %>%
	arrange( desc( adiff ))

c %>%  mutate( diff =  ( unit_wt.x - unit_wt.y), adiff=abs(diff)  ) %>%
	filter( adiff>1) %>%
	arrange( desc( adiff ))


c

mofi %>% filter( is.na( lga ))
mofi %>% filter( is.na( pin ))
#mofi %>% filter( is.na( pin )) %>% summarise(sum(quantity))

mofi %>% distinct( pin ) %>% count()
df %>% distinct( pin ) %>% count()

mofi %>% 
  distinct( pin ) %>%
  anti_join( df %>% distinct( pin ))

df %>% 
  distinct( pin ) %>%
  anti_join( mofi %>% distinct( pin ))

#mofi %>% filter( pin == "569726394")


mofi %>% distinct( lga ) %>% count() 
df %>% distinct( lga ) %>% count()

mofi %>% 
  distinct( lga ) %>%
  anti_join( df %>% distinct( lga ))
df %>% 
  distinct( lga ) %>%
  anti_join( mofi %>% distinct( lga ))




# show differences between 2 datasets, when groupped on group, joined on group, for sum(value)
show_differences <- function(df1, df2, group, value) {

  group_quo = enquo(group)
  group = group_quo[2] %>% as.character()
  value = enquo(value)

  df1 %>% group_by(!!group_quo) %>% 
    summarise(v1 := sum(!!value)) -> a
  df2 %>% group_by(!!group_quo) %>% 
    summarise(v2 := sum(!!value)) -> b

  a %>% distinct( !!group_quo ) %>% anti_join( b, by=group) %>% print()
  b %>% distinct( !!group_quo ) %>% anti_join( a, by=group) %>% print()

  inner_join( a, b, by=group ) %>%
  mutate( diff = ( v1 - v2), adiff=abs(diff)  ) %>%
    filter( adiff>1) %>%
    arrange( desc( adiff )) 
}

debug(show_differences)
show_differences(df,mofi, pin, quantity)
show_differences(df,mofi, pin, unit_wt)
show_differences(df,mofi, pin, ddd_mg_factor)
show_differences( df,  mofi, pin, n_dose)
show_differences( df,  mofi, supply_year, n_dose)

show_differences( df_patient_dose,  mofi, pin, n_dose)

show_differences( df_patient_dose,  df, pin, n_dose)
show_differences( mofi,  df, pin, n_dose)

show_differences(
                 df %>% distinct( item_code, unit_wt),
                 mofi %>% distinct( item_code, unit_wt), 
                 item_code, 
                 unit_wt)

show_differences(
                 df %>% distinct( item_code, ddd_mg_factor),
                 mofi %>% distinct( item_code, ddd_mg_factor), 
                 item_code, 
                 ddd_mg_factor)


df_patient_dose %>%
  inner_join( df_patient_usage ) %>%
  inner_join( df_patient ) %>%
  ungroup() -> a


show_differences( a, mofi, pin, n_dose)

show_differences(df,mofi, age, quantity)

