
---
title: "Check"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-04-30"
output: 
  word_document:
    reference_docx: ../../common/word_reference_style.docx
---


```{r set-options, echo=FALSE, cache=FALSE, warning=FALSE, results='hide'}
rm(list=ls())
options(width = 200)
show_code = FALSE
setwd("~/mydoc/research/mofi/continuing/R")
source("functions.R")
source("get_data.R")
source("generate_data_frames.R")
source("standardisation.R")
```
#Methods

```{r data_preparation, echo=FALSE, cache=FALSE, results="hide", warning=FALSE}

data.cache( generate_data_frames, frequency='yearly')

readstata13::read.dta13( 'check/Output_for_Dennis.dta') %>%
  as.tibble() %>%
  rename( lga=LGA,
         pin=ID, 
         sex=gender,
         quantity=qty,
         quarter=dup,
         supply_date=DateSupply,
         unit_wt = Unit_wt,
         ddd_mg_factor = DDD,
		 item_code = Item_code 
         )  %>%
  mutate( state=str_trim( state ),
        age = age_grouping_mofi( age),
        lga = as.character( lga ) ,
		item_code = str_trim(item_code ), 
        unit_wt=ifelse( item_code=='02124T', 2000, unit_wt),
		ddd_mg_factor=ifelse( item_code=='08423H', 4, ddd_mg_factor),
        n_dose=quantity * unit_wt / ddd_mg_factor ,
        supply_year=as.factor(substring( supply_date,6,9 ))
        )  %>%
  filter( lga != '89399' & state!='ACT' & item_code != '91194Q' ) %>% 
  { . } -> mofi


```

#powerpoint slide 1

```{r ppt_1, echo=TRUE}


df_patient_dose %>%
  inner_join( df_patient_usage ) %>%
  inner_join( df_patient ) %>%
  ungroup() -> df_initial


df_initial %>%
  filter( lga==10050) %>%
  select_and_standardise_ddd(standardise_over=qw('lga usage_category'), 
                             join_with= c('supply_year'), 
                             f_join_population
                             ) %>% ungroup() %>% summarize( sum(ddd) )

df_initial %>%
  filter( lga==10050) %>%
  select_and_standardise_ddd(standardise_over=qw('lga'), 
                             join_with= c('supply_year'), 
                             f_join_population
                             ) 
df_initial %>%
  filter( lga==10050) %>%
  select_and_standardise_ddd(standardise_over=qw('lga usage_category'), 
                              join_with= c('supply_year'), 
                              f_join_population
                              ) 

standardise_using <- qw("age sex")  %>%   
  setdiff( standardise_over ) %>% 
    setdiff( join_with )


a %>%
  ungroup() %>%
  filter( lga==10050) %>%
  filter( usage_category=='regular') %>%
  filter( supply_year=='2013') %>%
  group_by( lga, supply_year, age, sex, usage_category ) %>%
  summarise( n_dose = sum(n_dose)) %>%
  f_join_population( rollup_level=qw('lga supply_year age sex')) %>% 
  mutate( ddd = (n_dose * 1000 * 10) / (population * my_year_length( supply_year ) )) %>%  
  select( -population ) %>%
  f_join_population( rollup_level=qw('supply_year age sex')) %>%  # get totals for each lga
  mutate( ddd_standardized = ddd * population ) %>%  
  select( -population ) %>%
  group_by( lga, supply_year, usage_category ) %>%
  summarise( ddd_standardized = sum(ddd_standardized )) %>%
  f_join_population ( c('supply_year') ) %>% 
  # divide by the total population, and standardisation finished
  mutate( ddd = ddd_standardized / population ) %>%  
  select( lga, supply_year, usage_category, ddd ) %>%
  ungroup()

a %>%
  ungroup() %>%
  filter( supply_year=='2013') %>%
  group_by( supply_year, age, sex, usage_category ) %>%
  summarise( n_dose = sum(n_dose)) %>%
  f_join_population( rollup_level=qw('supply_year age sex')) %>% 
  mutate( ddd = (n_dose * 1000 * 10) / (population * my_year_length( supply_year ) )) %>%  
  select( -population ) %>%
  f_join_population( rollup_level=qw('supply_year age sex')) %>%  
  mutate( ddd_standardized = ddd * population ) %>%  
    select( -population ) %>%
    group_by( supply_year, usage_category ) %>%
    summarise( ddd_standardized = sum(ddd_standardized )) %>%
    f_join_population ( c('supply_year') ) %>% 
    # divide by the total population, and standardisation finished
    mutate( ddd = ddd_standardized / population ) %>%  
    select( supply_year, usage_category, ddd ) %>%
    ungroup()

# code to show individual level differences
mofi %>% distinct( item_code, unit_wt) %>% filter( item_code=='02124T')
mofi %>% filter( pin == 17639347) %>% View
df %>% filter( pin == 17639347) %>% View
df_patient_dose %>% filter( pin == 21792435) %>% View

mofi %>% group_by( pin ) %>% summarize( sm=sum(quantity * unit_wt / ddd_mg_factor) ) -> a
df %>% group_by( pin ) %>% summarize( sd=sum(n_dose) ) -> b

a %>% inner_join( b , by='pin' ) -> c

c %>%  mutate( diff = (sd - sm), adiff=abs(diff)  ) %>%
	filter( adiff>1) %>%
	arrange( desc( adiff )) -> d

df %>%
  inner_join( d, by='pin') %>%
  count( type_name, item_code, sort=TRUE)




df %>% summarize( sum(quantity) )
mofi %>% summarize( sum(quantity) )

df %>% summarize( sum(n_dose) )
mofi %>% summarize( sum(ddd_mg_factor, na.rm=TRUE) )

df %>% distinct( lga ) %>% count()


mofi %>%  filter( is.na(lga) ) %>% count()
df %>% filter( lga=='.') %>% count() 



intersect(a,b) 
setdiff(a,b) 
setdiff(b,a) 

mofi %>% distinct( pin ) %>% setdiff( df %>% distinct( pin ))
mofi  %>% filter( !( supply_date, 5 )  %>% distinct( pin ) %>% setdiff( df %>% distinct( pin ))
df %>% distinct( pin ) %>% setdiff( mofi %>% distinct( pin ))

mofi %>% filter( pin==74301)

df





a %<>% as.tibble( a) 


population=read.dta13( 'check/nsw_vic_populato_and_seifa_data.dta')





df_patient_type %>%
	inner_join( df_patient_usage ) %>%
	inner_join( df_patient ) %>%
	select( pin, usage_category, supply_year, age, sex, n_dose) %>% 
	select_and_standardise_ddd( standardise_over=qw( "age supply_year usage_category" )) %>%
	mutate( year_age  = paste( age,supply_year) ) %>%
	select( -supply_year, -age ) %>%
	mutate( ddd=round(ddd,2)) %>%
	spread( year_age, ddd ) %>%
	write.csv('/tmp/a.csv')

	kable() %>% clipr::write_clip()


	df_patient_dose %>%
		inner_join( df_patient_usage ) %>%
		inner_join( df_patient ) %>%
		group_by( state, usage_category, supply_year) %>% 
		summarise( n_dose = sum( n_dose ) )  %>%
		join_population_grouped( qw("state supply_year")) %>% 
		ungroup() %>%
		mutate( ddd = (n_dose * 1000 * 10) / (person_days)) %>% 
		mutate( year_age  = paste( state, supply_year) ) %>%
		select( ddd, usage_category, year_age) %>%
		mutate( ddd=round(ddd,2)) %>%
		spread( year_age, ddd ) %>%
		write.csv('/tmp/b.csv')

		ungroup() %>%
		print()

