
---
title: "Check"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-04-30"
output: 
  word_document:
    reference_docx: ../../common/word_reference_style.docx
---


```{r set-options, echo=FALSE, cache=FALSE, warning=FALSE, results='hide'}
rm(list=ls())
options(width = 200)
show_code = FALSE
setwd("~/mydoc/research/mofi/continuing/R")
source("functions.R")
source("get_data.R")
source("generate_data_frames.R")
source("standardisation.R")
```
#Methods

```{r data_preparation, echo=FALSE, cache=FALSE, results="hide", warning=FALSE}

data.cache( generate_data_frames, frequency='yearly')

```
#powerpoint slide 1
```{r ppt_1, echo=FALSE}


df %<>% filter( lga != '.')

#readstata13::read.dta13( 'check/vic_nsw_newVSint.dta') -> mofi

readstata13::read.dta13( 'check/Output_for_Dennis.dta') %>%
  as.tibble() %>%
  rename( lga=LGA,
         pin=ID, 
         sex=gender,
         quantity=qty,
         quarter=dup,
         supply_date=DateSupply,
         unit_wt = Unit_wt,
         ddd_mg_factor = DDD,
		 item_code = Item_code 
         )  %>%
  mutate( state=str_trim( state ),
        age = age_grouping_mofi( age),
        lga = as.character( lga ) ,
		item_code = str_trim(item_code ), 
        unit_wt=ifelse( item_code=='02124T', 2000, unit_wt),
		ddd_mg_factor=ifelse( item_code=='08423H', 4, ddd_mg_factor),
        n_dose=quantity * unit_wt / ddd_mg_factor ,
        supply_year=as.factor(substring( supply_date,6,9 ))
        )  %>%
  filter( lga != '89399' & state!='ACT' & item_code != '91194Q' ) %>% 
  { . } -> mofi


names(df) %>% setdiff( names( mofi ))
names(mofi) %>% setdiff( names( df ))

mofi %>% 
	filter( item_code == "08423H" ) %>% 
	select( item_code, GenerName, from_strenth, genricType, Item_type, ddd_mg_factor) %>% distinct( )                 


mofi %>% distinct( Unit)
mofi %>% distinct( unit_wt)
mofi %>% distinct( item_code)
mofi %>% distinct( Item_type)
mofi %>% distinct( genricType)

mofi %>% distinct ( item_code, unit_wt, ddd_mg_factor )   -> a
df %>% distinct ( item_code, unit_wt, ddd_mg_factor )  -> b
a %>% inner_join( b , by='item_code' ) -> c

c %>%  mutate( diff = (ddd_mg_factor.x - ddd_mg_factor.y), adiff=abs(diff)  ) %>%
	filter( adiff>.1) %>%
	arrange( desc( adiff ))

c %>%  mutate( diff =  ( unit_wt.x - unit_wt.y), adiff=abs(diff)  ) %>%
	filter( adiff>1) %>%
	arrange( desc( adiff ))


c

mofi %>% filter( is.na( lga ))



mofi %>% distinct( pin ) %>% count()
df %>% distinct( pin ) %>% count()

mofi %>% 
  distinct( pin ) %>%
  anti_join( df %>% distinct( pin ))
df %>% 
  distinct( pin ) %>%
  anti_join( mofi %>% distinct( pin ))

#mofi %>% filter( pin == "569726394")


mofi %>% distinct( lga ) %>% count() 
df %>% distinct( lga ) %>% count()

mofi %>% 
  distinct( lga ) %>%
  anti_join( df %>% distinct( lga ))
df %>% 
  distinct( lga ) %>%
  anti_join( mofi %>% distinct( lga ))




# show differences between 2 datasets, when groupped on group, joined on group, for sum(value)
show_differences <- function(df1, df2, group, value) {

  group_quo = enquo(group)
  group = group_quo[2] %>% as.character()
  value = enquo(value)

  df1 %>% group_by(!!group_quo) %>% 
    summarise(v1 := sum(!!value)) -> a
  df2 %>% group_by(!!group_quo) %>% 
    summarise(v2 := sum(!!value)) -> b

  a %>% distinct( !!group_quo ) %>% anti_join( b, by=group) %>% print()
  b %>% distinct( !!group_quo ) %>% anti_join( a, by=group) %>% print()

  inner_join( a, b, by=group ) %>%
  mutate( diff = ( v1 - v2), adiff=abs(diff)  ) %>%
    filter( adiff>1) %>%
    arrange( desc( adiff )) 
}

debug(show_differences)
show_differences(df,mofi, pin, quantity)
show_differences(df,mofi, pin, unit_wt)
show_differences(df,mofi, pin, ddd_mg_factor)
show_differences( df,  mofi, pin, n_dose)
show_differences( df,  mofi, supply_year, n_dose)

show_differences( df_patient_dose,  mofi, pin, n_dose)

show_differences( df_patient_dose,  df, pin, n_dose)
show_differences( mofi,  df, pin, n_dose)

show_differences(
                 df %>% distinct( item_code, unit_wt),
                 mofi %>% distinct( item_code, unit_wt), 
                 item_code, 
                 unit_wt)

show_differences(
                 df %>% distinct( item_code, ddd_mg_factor),
                 mofi %>% distinct( item_code, ddd_mg_factor), 
                 item_code, 
                 ddd_mg_factor)


show_differences( a, mofi, pin, n_dose)

show_differences(df,mofi, age, quantity)


#todo
df_patient_dose %>%
  inner_join( df_patient_usage ) %>%
  inner_join( df_patient ) %>%
  ungroup() -> a


a %>%
  filter( lga==10050) %>%
  select_and_standardise_ddd(standardise_over=qw('lga usage_category'), 
                             join_with= c('supply_year'), 
                             f_join_population
                             ) 

a %>%
  filter( lga==10050) %>%
  select_and_standardise_ddd(standardise_over=qw('lga'), 
                             join_with= c('supply_year'), 
                             f_join_population
                             ) 
  a %>%
    filter( lga==10050) %>%
    select_and_standardise_ddd(standardise_over=qw('lga usage_category'), 
                               join_with= c('supply_year'), 
                               f_join_population
                               ) 

    standardise_using <- qw("age sex")  %>%   # could also include supply_year except we never standardise on supply_year :-)
      setdiff( standardise_over ) %>% 
        setdiff( join_with )


a %>%
  ungroup() %>%
  filter( lga==10050) %>%
  group_by( lga, supply_year, age, sex, usage_category ) %>%
  summarise( n_dose = sum(n_dose)) %>%
  f_join_population( rollup_level=qw('lga supply_year age sex'))

      f_join_population ( c( standardise_over, join_with, standardise_using )) %>%
      mutate( proportion = (n_dose * 1000 * 10) / (population * my_year_length( supply_year ) )) %>%  # calculate proportion at this level

      # now that we have the proportion for each subgroup,
      # now we standardise that proportion based on the total population
      # first throw away extraneous variables brought in by previous join, 
      # eg population and person_days
      # all we want is the proportion,and the key variables

      select_( .dots = c(standardise_over, join_with, standardise_using, "proportion") ) %>%

        # get the population grouped by levels we want to standardise on, that is, 
        # the standardisation variables (possibly age and/or sex, as long as they are not
        # included in the non-standard_vars), and join_with, eg. supply_year

        # this next call differentiiates standardise_over and join_with, 
        # we rollup the pupulation by grouping on everything apart from the standardise_over
        # for example, we might put lga or state in standardise_over, and rollup to that
        f_join_population ( c(standardise_using,  join_with)) %>% 
        mutate( proportion_standardized = proportion * population ) %>%  

        # now, sum up our standardized_proportion, 
        # grouped on age and/or sex as long as we ae not using it elsewhere
        group_by_( .dots=c( standardise_over, join_with )) %>%  # no standardize_vars here
        summarise( proportion_standardized = sum(proportion_standardized )) %>%
          select_( .dots = c( standardise_over, join_with, "proportion_standardized") ) %>% # and cleanup

          # get population completely rolled up, so we can divide
          f_join_population ( join_with ) %>% 

            # divide by the total population, and standardisation finished
            mutate( ddd = proportion_standardized / population ) %>%  

            # finished standardisation, cleanup by selecting only variables of interest
            select_( .dots = c(standardise_over, join_with, "ddd") ) %>%
            ungroup()
}

# code to show individual level differences
mofi %>% distinct( item_code, unit_wt) %>% filter( item_code=='02124T')
mofi %>% filter( pin == 17639347) %>% View
df %>% filter( pin == 17639347) %>% View
df_patient_dose %>% filter( pin == 21792435) %>% View

mofi %>% group_by( pin ) %>% summarize( sm=sum(quantity * unit_wt / ddd_mg_factor) ) -> a
df %>% group_by( pin ) %>% summarize( sd=sum(n_dose) ) -> b

a %>% inner_join( b , by='pin' ) -> c

c %>%  mutate( diff = (sd - sm), adiff=abs(diff)  ) %>%
	filter( adiff>1) %>%
	arrange( desc( adiff )) -> d

df %>%
  inner_join( d, by='pin') %>%
  count( type_name, item_code, sort=TRUE)




df %>% summarize( sum(quantity) )
mofi %>% summarize( sum(quantity) )

df %>% summarize( sum(n_dose) )
mofi %>% summarize( sum(ddd_mg_factor, na.rm=TRUE) )

df %>% distinct( lga ) %>% count()


mofi %>%  filter( is.na(lga) ) %>% count()
df %>% filter( lga=='.') %>% count() 



intersect(a,b) 
setdiff(a,b) 
setdiff(b,a) 

mofi %>% distinct( pin ) %>% setdiff( df %>% distinct( pin ))
mofi  %>% filter( !( supply_date, 5 )  %>% distinct( pin ) %>% setdiff( df %>% distinct( pin ))
df %>% distinct( pin ) %>% setdiff( mofi %>% distinct( pin ))

mofi %>% filter( pin==74301)

df





a %<>% as.tibble( a) 


population=read.dta13( 'check/nsw_vic_populato_and_seifa_data.dta')





df_patient_type %>%
	inner_join( df_patient_usage ) %>%
	inner_join( df_patient ) %>%
	select( pin, usage_category, supply_year, age, sex, n_dose) %>% 
	select_and_standardise_ddd( standardise_over=qw( "age supply_year usage_category" )) %>%
	mutate( year_age  = paste( age,supply_year) ) %>%
	select( -supply_year, -age ) %>%
	mutate( ddd=round(ddd,2)) %>%
	spread( year_age, ddd ) %>%
	write.csv('/tmp/a.csv')

	kable() %>% clipr::write_clip()


	df_patient_dose %>%
		inner_join( df_patient_usage ) %>%
		inner_join( df_patient ) %>%
		group_by( state, usage_category, supply_year) %>% 
		summarise( n_dose = sum( n_dose ) )  %>%
		join_population_grouped( qw("state supply_year")) %>% 
		ungroup() %>%
		mutate( ddd = (n_dose * 1000 * 10) / (person_days)) %>% 
		mutate( year_age  = paste( state, supply_year) ) %>%
		select( ddd, usage_category, year_age) %>%
		mutate( ddd=round(ddd,2)) %>%
		spread( year_age, ddd ) %>%
		write.csv('/tmp/b.csv')

		ungroup() %>%
		print()

