---
title: "Hypothesis 3"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-04-30"
output: 
  word_document:
    reference_docx: ../../common/word_reference_style.docx
  html_document:
    code_folding: hide
---


```{r set-options, echo=FALSE, cache=FALSE, warning=FALSE, results='hide'}
rm(list=ls())
library(workflowr)
options(width = 200)
show_code = FALSE
source("lib/functions.R")
source("lib/standardisation.R")
source("lib/get_data.R")
source("lib/generate_data_frames.R")

states=c(1,2)
source("lib/mapping.R")

source("lib/mapping_paper.R")

#df_mapdata = read.csv('data/Data2MapFromMofi.csv') %>% as.tibble()

```
#Methods

```{r data_preparation, echo=FALSE, cache=FALSE, results="hide", warning=FALSE}

data.cache( generate_data_frames, frequency='yearly')

df_population %<>% mutate( seifa=plyr::revalue(seifa, c('Least'='Low'))) 
###############################################################
```

maps  - now need to generate mapdata

lgas in 4th quartile of dispensing - Figure 3


```{r}

df %>%
  count( type_name, ddd_mg_factor ) 


df_population %>%
  distinct( lga )

df_population %>%
  group_by(supply_year, state) %>%
  summarise( sum( population ))

df %>%
  select_and_standardise_ddd (  standardise_over=qw('lga supply_year')  ) %>%
  group_by( supply_year ) %>%
  mutate( quartile = cut( ddd, quantile( ddd, type=2), labels=1:4 ) )%>%
  ungroup() %>%
  filter( quartile=='4') %>%
  count( lga ) %>% 
  { . } -> df_lgas_in_fourth_quartile

df_lgas_in_fourth_quartile %>%
   count( n ) %>%
   rename( years_in_fourth_quartile = n, count_lga = nn)


 df_population %>%
   distinct( lga,state) %>%
   inner_join( df_lgas_in_fourth_quartile ) %>%
   count( state)

```
lgas in 4th quartile of dispensing  for chronic users - Figure 4

```{r}

df %>%
  inner_join( df_patient_usage ) %>%
  filter( usage_category =='chronic') %>%
  select_and_standardise_ddd (  standardise_over=qw('lga supply_year')  ) %>%
  group_by( supply_year ) %>%
  mutate( quartile = cut( ddd, quantile( ddd), labels=1:4 ) )%>%
  ungroup() %>%
  filter( quartile=='4') %>%
  count( lga ) %>% 
  { . } -> df_chronic_lgas_in_fourth_quartile

df_chronic_lgas_in_fourth_quartile %>%
  count( n ) %>%
  rename( years_in_fourth_quartile = n, count_lga = nn)


df_population %>%
  distinct( lga,state) %>%
  inner_join( df_chronic_lgas_in_fourth_quartile ) %>%
  count( state)

```

```{r}

df_population %>% 
  distinct( lga, urbanization ) %>%
  append_data( base_map, 
              ., 
              key.shp="LGA_CODE11", 
              key.data="lga" 
              )  %>%
  tm_shape( ) + 
  tm_polygons( "urbanization", 
              ) +
tm_layout(frame=FALSE,
          legend.position = c("right", "top"), bg.color="#FFFFFF",
          inner.margins = c(.25,.02,.02,.25)  )



df_lgas_in_fourth_quartile %>%
  rename( Value = n ) %>%
  printMap( title = "Number of years\nthe regular users\nwere in the\nhighest quartile",
                                                filename = '/tmp/regular.png' )

  df_chronic_lgas_in_fourth_quartile %>%
  rename( Value = n ) %>%
  printMap( title = "Number of years\nthe total quantity\ndispensed to \n chronic users were in\nthe fourth quartile",
           filename = '/tmp/fourthQuartile.png' )



```

#Results for the paper

% for each usage category

```{r}

df_patient_usage %>%
  count( usage_category ) %>%
  mutate( pct = round( n/sum(n) * 100,2 )) %>% 
  kable()

```

```{r}


df_patient %>%
  count( sex ) %>%
  mutate( pct = round( n/sum(n) * 100,2 )) %>% 
  kable()


```
drug type by number of people and drug type 
```{r}

df_patient %>% count() %$% n -> npin


df %>%
  distinct( type_name, pin ) %>%
  count( type_name ) %>%
  mutate( pct = round( n/npin * 100,2 )) %>% 
  kable()


df %>%
  select_and_standardise_ddd (  standardise_over=qw('state type_name') , join_with=qw('supply_year') ) %>%
  count( type_name ) %>%
  mutate( pct = round( n/sum(n) * 100,2 )) %>% 
  kable()
```

DDD/1000 by drug type standardised
```{r}


df %>%
  select_and_standardise_ddd (  standardise_over=qw('state type_name') , join_with=qw('supply_year') ) %>%
  filter( supply_year == '2016') %>%
  select(  -supply_year) %>%
  spread( state, ddd)  %>% 
  kable()


```
mean doses by cateogry
```{r}

df %>%
  inner_join( df_patient_usage ) %>%
  group_by( usage_category ) %>%
  summarise( round( mean( n_dose ), 1 ))  %>% 
  kable()


```
mean doses by seifa
```{r}

df %>%
  inner_join( df_population %>% distinct( lga, seifa )) %>%
  group_by( seifa ) %>%
  summarise( n_dose = round( mean( n_dose ),1) ) %>% 
  kable()


```

#IRR content - TODO

Avg ddd / lga ; and bootstrapped confidence intervals


```{r}
library(rcompanion)
df %>%
  select_and_standardise_ddd (  standardise_over=qw('lga')  ) %>%
  ggplot( aes( ddd, group=1) ) + geom_histogram(bins=60)

df %>%
  select_and_standardise_ddd (  standardise_over=qw('lga')  ) %>%
  groupwiseGeometric( ddd ~ 1, ., conf   = 0.95,
                digits = 6,
                R      = 10000,
                boot        = TRUE,
                traditional = FALSE,
                normal      = FALSE,
                basic       = FALSE,
                percentile  = FALSE,
                bca         = TRUE )

df %>%
  select_and_standardise_ddd (  standardise_over=qw('lga')  ) %$%
  t.test( ddd )

df %>%
  select_and_standardise_ddd (  standardise_over=qw('lga')  ) %>%
  summarise( se = sd( ddd ) / sqrt( length(ddd)))

df %>%
  select_and_standardise_ddd (  standardise_over=qw('lga')  ) %>%
  summarise( mean( ddd ), max(ddd), min(ddd))

```



## Table 2 - Mixed effects model
```{r lme}

library(haven)

library(lme4)

df_population %>%
  distinct( lga, seifa, urbanization ) %>% 
  { . } -> df_lga

df %>%
  distinct( pin, quarter, supply_year) %>%
  count( pin, supply_year  ) %>%
  inner_join( df_patient ) %>% 
  inner_join( df_lga ) %>%
  mutate( supply_year = as.ordered( supply_year )) %>%
  glmer( n~ sex+age+supply_year+seifa+urbanization + (1|state/lga), data=.) %>% 
  { . } -> model

summary(model)
```





## FIgure 2
mean doses by # quarters using
```{r}



df%>%
  inner_join( df_patient_usage ) %>%
  group_by( usage_category, supply_year ) %>%
  summarise( n_dose = round( mean( n_dose ),1) ) %>% 
  ggplot( aes( x=supply_year, y=n_dose, fill=usage_category  ) )+
  geom_col( position='dodge') +
  ylab( "Total quantity (in DDD unit) per prescription" ) + 
  xlab('')



```

##Table 1
ddd / year (standardised) for each year by user_type
```{r}

df %>%
  inner_join( df_patient_usage ) %>%
  select_and_standardise_ddd (  standardise_over=qw('state usage_category supply_year') , join_with=qw('supply_year') ) %>%
  mutate( ddd = round(ddd, 2 ), u_s = paste( usage_category, state)) %>% 
  select(-state, -usage_category) %>%
  group_by( u_s, supply_year ) %>%
  summarise( ddd=sum(ddd))  %>%
  spread( u_s, ddd)  %>% 
  kable()

df %>%
  inner_join( df_patient_usage ) %>%
  select_and_standardise_ddd (  standardise_over=qw('state usage_category') , join_with=qw('supply_year') ) %>%
  mutate( ddd = round(ddd, 2 ), u_s = paste( usage_category, state)) %>% 
  select(-state, -usage_category) %>%
  group_by( u_s ) %>%
  summarise( ddd=sum(ddd))  %>%
  spread( u_s, ddd)  %>% 
  kable()

df %>%
  inner_join( df_patient_usage ) %>%
  select_and_standardise_ddd (  standardise_over=qw('state') , join_with=qw('supply_year') ) %>%
  mutate( ddd = round(ddd, 2 )) %>% 
  spread( state, ddd)  %>% 
  kable()

```

