---
title: "Ongoing Opioid Usage Data Exploration"
author:  "Dennis Wollersheim"
date: "2018-04-11"
output: 
  word_document:
    reference_docx: ../../common/word_reference_style.docx
---


```{r set-options, echo=FALSE, cache=FALSE, warn=FALSE}
rm(list=ls())
options(width = 200)
show_code = FALSE
setwd("~/mydoc/research/mofi/continuing/R")
source("functions.R")
```
#Methods

```{r data_preparation, echo=FALSE, cache=FALSE, results="hide", warn=FALSE}

df <- get_continuing_df('continuing') %>%
  filter(state %in% c("NSW", "VIC"))
# 
# list all schemes
df %>% 
  select( pin, scheme ) %>%
  unique() %>%
  group_by(pin) %>% 
  summarise( all_scheme=paste(sort(scheme), collapse=','))  %>%
  {.} -> df_patient_scheme
#
# select out patients
#

df %>% 
  select (pin, gender, age, state) %>% 
  unique()  %>%
  join( df_patient_scheme, by="pin") %>%
  as.tibble() %>%
  {.} -> df_patients
#

df %<>% 
	select( -gender, -age, -state, -scheme ) %>%
	mutate( quarter = quarter(supply_date, with_year = TRUE))

```

<!---
	Patients who were dispensed at least in 15 quarters were identified as regular users.
Patients who were dispensed at least in 9 quarters were identified as long-term users.
Patients who were dispensed 1-8 quarters were identified as short-term users.
Patients who were dispensed just one occasion only were identified as one off users.
--->
```{r}

df%>%
	group_by(pin,  type_name) %>%
	summarise( n_dose = sum(no_doses),
			  quantity = sum(quantity),
			  n_script = n(),
			  n_quarter = n_distinct( quarter ),
			  n_quarter_tmp = ifelse( n_script==1, 0, n_quarter ),
			  usage_category= cut( n_quarter_tmp, 
								  c(-1, 0,8,14, 999999), 
								  labels = qw("one-off short-term long-term regular")
								  ) ) %>%
	select( -n_quarter_tmp ) %>%
	{.} -> df_patient_type

df%>%
  group_by(pin) %>%
  summarise( n_dose = sum(no_doses),
			quantity = sum(quantity),
			n_script = n(),
			n_quarter = n_distinct( quarter ),
			n_quarter_tmp = ifelse( n_script==1, 0, n_quarter ),
			usage_category= cut( n_quarter_tmp, 
							c(-1, 0,8,14, 999999), 
							labels = qw("one-off short-term long-term regular")
							) ) %>%
  			select( -n_quarter_tmp ) %>%
			{.} -> df_patient_usage

```

# distribution of the different drug genders, total count and percent
```{r, echo=FALSE}
df_patients  %>% 
  join( df_patient_usage, by=c("pin")) %>%
  as.tibble()  %>%
  filter(state %in% c("NSW", "VIC")) %$%
  table(.$gender, .$state) %>%
  prop.table( 2) %>% `*` (100) %>% round(2) %>%
  kable()

df_patients  %>% 
  join( df_patient_usage, by=c("pin")) %>%
  as.tibble()  %>%
  ggplot( ) + 
  geom_bar( mapping=aes(x=state, fill=gender), stat="count" ) + 
  ggtitle("") 

```


# distribution of the different drug users, total count and percent
```{r, echo=FALSE}
df_patients  %>% 
  join( df_patient_usage, by=c("pin")) %>%
  as.tibble()  %>%
  group_by( usage_category) %>%
  summarize( n_patients = n()) %>%
  mutate( proportion = round(n_patients / sum(n_patients),4) * 100 ) %>%
  kable()

df_patients  %>% 
  join( df_patient_usage, by=c("pin")) %>%
  as.tibble()  %>%
  ggplot( ) + 
  geom_bar( mapping=aes(x=state, fill=usage_category), stat="count" ) + 
  ggtitle("") 
```

# distribution of the different user types by drug type, in percent for each drug type
### note this is different from the user types above, because it is broken down by drug
```{r, echo=FALSE}
df_patients  %>% 
  join( df_patient_type, by=c("pin")) %>%
  as.tibble()  %$%
  table(.$usage_category, .$type_name) %>%
  prop.table( 2) %>% `*` (100) %>% round(2) %>%
  kable()

df_patients  %>% 
  join( df_patient_type, by=c("pin")) %>%
  as.tibble()  %>%
  ggplot( ) + 
  geom_bar( mapping=aes(x=state, fill=usage_category), stat="count" ) + 
  ggtitle("User counts for each state, drug type and user category") +
  facet_wrap(~type_name , scales="free") 
```

# distribution of the different user types by gender, in percent for each gender
```{r, echo=FALSE}
df_patients  %>% 
  join( df_patient_usage, by=c("pin")) %>%
  as.tibble()  %$%
  table(.$usage_category, .$gender) %>%
  prop.table( 2) %>% `*` (100) %>% round(2) %>%
  kable()

df_patients  %>% 
  join( df_patient_usage, by=c("pin")) %>%
  as.tibble()  %>%
  ggplot( ) + 
  geom_bar( mapping=aes(x=state, fill=usage_category), stat="count" ) + 
  ggtitle("User counts for each state, gender type and user category") +
  facet_wrap(~gender , scales="free") 

```

# distribution of the different user types by age_group, in percent for each age group
```{r, echo=FALSE}
df_patients  %>% 
  join( df_patient_usage, by=c("pin")) %>%
  mutate( age_group= age_grouping( age, 20 )) %>%
  as.tibble()  %$%
  table(.$usage_category, age_group) %>%
  prop.table( 2) %>% `*` (100) %>% round(2) %>%
  kable()

df_patients  %>% 
  join( df_patient_usage, by=c("pin")) %>%
  as.tibble()  %>%
  mutate( age_group= age_grouping( age, 20 )) %>%
  ggplot( ) + 
  geom_bar( mapping=aes(x=state, fill=usage_category), stat="count" ) + 
  ggtitle("User counts for each state, age group and user category") +
  facet_wrap(~age_group , scales="free") 
```

# distribution of the different user types by payment scheme, in percent for each payment scheme
# note, some people have more than one payment scheme
```{r, echo=FALSE}
df_patients  %>% 
  join( df_patient_usage, by=c("pin")) %>%
  as.tibble()  %$%
  table(.$usage_category, .$all_scheme) %>%
  prop.table( 2) %>% `*` (100) %>% round(2) %>%
  kable()

df_patients  %>% 
  join( df_patient_usage, by=c("pin")) %>%
  as.tibble()  %>%
  ggplot( ) + 
  geom_bar( mapping=aes(x=state, fill=usage_category), stat="count" ) + 
  ggtitle("User counts for each state, payment scheme and user category") +
  facet_wrap(~all_scheme , scales="free") 
```

```

