---
title: "Hypothesis 1"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-04-30"
output: 
  word_document:
    reference_docx: word_reference_style.docx
---
```{r}

getwd()
```


```{r results='hide', message=FALSE, warning=FALSE}




rm(list=ls())
options(width = 200)
show_code = FALSE
getwd()
source("lib/functions.R")
source("lib/standardisation.R")
source("lib/get_data.R")
source("lib/generate_data_frames.R")
```
#Methods

```{r results='hide', message=FALSE, warning=FALSE}


data.cache( generate_data_frames )

```

# Methods
Patients who were dispensed at least in 15 quarters were identified as regular users.
Patients who were dispensed at least in 9 quarters were identified as long-term users.
Patients who were dispensed 1-8 quarters were identified as short-term users.
Patients who were dispensed just one occasion only were identified as one off users.



#Distribution of types of users in two states, stratified by age-group and sex
```{r user_type_by_age_sex_state, echo=FALSE}

df_patient  %>% 
	inner_join( df_patient_usage, by=c("pin")) %>%
	group_by( state, age, sex ) %>%
	summarize( n_patients = n()) %>%
	ungroup() %>%
	mutate( state_sex=paste( state, sex, sep='_')) %>%
	select(-state, -sex ) %>%
	spread(state_sex, n_patients) %>%
	arrange( age ) %>%
	kable()

```

#Distribution of types of users in two states, group proportion for the state and sex
```{r user_type_by_age_sex_state_prop1, echo=FALSE}

df_patient  %>%
	inner_join( df_patient_usage, by=c("pin")) %>%
	select( state, age, sex ) %>%
	mutate( state_sex=paste( state, sex, sep='_')) %>%
	group_by(state_sex, age )  %>%
	summarise( n=n()) %>%
	group_by(state_sex)  %>%
	mutate(  freq = round(n / sum(n)*100,2) ) %>%
	select(-n) %>%
	spread( state_sex, freq) %>%
	kable()

```

#Distribution of types of users in two states, group proportion for the age group
```{r user_type_by_age_sex_state_prop2, echo=FALSE}

df_patient  %>%
	inner_join( df_patient_usage, by=c("pin")) %>%
	select( state, age, sex ) %>%
	mutate( state_sex=paste( state, sex, sep='_')) %>%
	group_by(state_sex, age )  %>%
	summarise( n=n()) %>%
	group_by(age)  %>%
	mutate(  freq = round(n / sum(n)*100,2) ) %>%
	select(-n) %>%
	spread( state_sex, freq) %>%
	kable()

```


#What proportion of prescriptions and DDDs are consumed by the regular, long-term, short-term and one-off users? - combined and state-wise

## Combined NSW and VIC total scripts first first

```{r ddd_by_usertype_combined, echo=FALSE}
df_patient_dose %>%
  group_by(pin) %>%
  summarise(n_script = sum( n_script ) ) %>%
  inner_join( df_patient, by=c('pin')) %>%
  inner_join( df_patient_usage, by=c("pin")) %>%
  group_by( usage_category ) %>%
  summarise(  n_script=sum(n_script)) %>%
  kable()

```	

## State level # of scripts total 

```{r scripts_by_usertype_state, echo=FALSE}

df_patient_dose %>%
  group_by(pin) %>%
  summarise(n_script = sum( n_script ) ) %>%
  inner_join( df_patient, by=c('pin')) %>%
	inner_join( df_patient_usage, by=c("pin")) %>%
	select( state, usage_category, n_script) %>%
	group_by(state, usage_category)  %>%
	summarise( n_script = sum(n_script)) %>%
	spread( state, n_script) %>%
	kable()

```	

## State level total scripts  percentage of total

```{r ddd_by_usertype_state_proportion, echo=FALSE, warning=FALSE}


df_patient_dose %>%
  group_by(pin) %>%
  summarise(n_script = sum( n_script ) ) %>%
  inner_join( df_patient, by=c('pin')) %>%
	inner_join( df_patient_usage, by=c("pin")) %>%
	select( state, usage_category, n_script) %>%
	group_by(state, usage_category)  %>%
	summarise( n_script = sum(n_script)) %>%
	group_by(state)  %>%
	mutate(  prop = round(n_script / sum(n_script)*100,2) ) %>%
	select(-n_script) %>%
	spread( state, prop) %>%
	kable()

```	

## State level DDD actual standardised

```{r ddd_by_usertype_state_actual, echo=FALSE, warning=FALSE}
debug(select_and_standardise_ddd)


df_patient_dose %>%
  group_by(pin, supply_year) %>%
  summarise(n_dose = sum( n_dose ) ) %>%
  inner_join( df_patient, by=c('pin')) %>%
  inner_join( df_patient_usage, by=c("pin")) %>%
	select_and_standardise_ddd( standardise_over=qw( "state" ), join_with=qw("usage_category supply_year") ) %>%
	spread( state, ddd) %>%
	kable()

 ```

 ## State level DDD proportion % of state total

```{r ddd_by_usertype_state_prop, echo=FALSE, warning=FALSE}
df_patient_dose %>%
  group_by(pin, supply_year) %>%
  summarise(n_dose = sum( n_dose ) ) %>%
  inner_join( df_patient, by=c('pin')) %>%
  inner_join( df_patient_usage, by=c("pin")) %>%
	select_and_standardise_ddd( standardise_over=qw( "state" ), 
	                           join_with=qw("usage_category supply_year") ) %>%
	group_by(state)  %>%
	mutate(  prop = round(ddd / sum(ddd)*100,2) ) %>%
	select(-ddd) %>%
	spread( state, prop) %>%
	kable()

```

#Is there any trend in type of users on type of opioids? E.g. regular users use xxx more than others etc.

```{r linear_model, echo=FALSE, warning=FALSE}

modelFormula = usage_category ~ all_scheme+sex++age+population+seifa+urbanization
df_patient  %>%
	inner_join( df_patient_usage, by=c("pin")) %>%
	mutate(all_scheme=as.factor(all_scheme)) %>%
	f_join_population( rollup_level= qw("seifa urbanization lga"), 
							join_key=qw("lga"))  %>%
	clm( modelFormula, data=. ) %>%
	{.} -> model
summary(model)

```

# plotting usage_category and population, raw and proportional

```{r Population_vs_category, echo=FALSE}
df_patient  %>%
	inner_join( df_patient_usage, by=c("pin")) %>%
	f_join_population( rollup_level= qw("seifa urbanization lga"), 
							join_key=qw("lga"))  %>%
	{.} -> ds

ds %>% ggplot( mapping=aes(x=population, fill=usage_category)) + geom_density(alpha=0.5)

ds %>% ggplot( mapping=aes(y=population, x=usage_category)) + geom_boxplot()

```

# plotting usage_category and scheme, both raw and proportional

```{r category_vs_scheme, echo=FALSE}

ds %>% ggplot( aes( usage_category, ..count..)) + geom_bar(aes(fill=all_scheme))

ds %>% ggplot( aes( usage_category, ..count..)) + geom_bar(aes(fill=all_scheme), position='fill')

```



# plotting usage_category and age, both raw and proportional

```{r category_vs_age, echo=FALSE}

ds %>% ggplot( aes( usage_category, ..count..)) + geom_bar(aes(fill=age))

ds %>% ggplot( aes( usage_category, ..count..)) + geom_bar(aes(fill=age), position='fill')

```


# plotting usage_category and seifa, both raw and proportional

```{r category_vs_seifa, echo=FALSE}

ds %>% ggplot( aes( usage_category, ..count..)) + geom_bar(aes(fill=seifa))

ds %>% ggplot( aes( usage_category, ..count..)) + geom_bar(aes(fill=seifa), position='fill')


```

# plotting usage_category and urbanisation, raw and proportional

```{r cateory_vs_urbanisation, echo=FALSE}
ds %>% ggplot( aes( usage_category, ..count..)) + geom_bar(aes(fill=urbanization))

ds %>% ggplot( aes( usage_category, ..count..)) + geom_bar(aes(fill=urbanization), position='fill')

```

#Identify the LGAs that have higher RATE of regular and long-term users (proportional to population)
# after standardization for age and sex.

```{r lga_by_certain_user_types, echo=FALSE}
#
#df_patient  %>%
#	inner_join( df_patient_usage, by=c("pin")) %>%
#	group_by( lga, usage_category, age, sex ) %>%
#	summarise( n_user = n()) %>%
#	filter(is_geographic_LGA(lga)) %>%
#	filter( as.integer(usage_category) > 2 ) %>%
#	simple_standardise_value( standardise_using=qw( "age sex" ), 
#								 standardise_across=qw("lga"), 
#								 count_var=.$n_user ) %>%
#	group_by( usage_category ) %>%
#	mutate( usage_level = cut( proportion, 4, 
#							  qw("low medium high very_high"), 
#							  ordered=TRUE )) %>%
#	ungroup() %>%
#	{.} -> df_lga_summary
##


print_map_set = function( target_category, name ) {
	df_lga_summary %>% 
		filter( as.integer(usage_category)==target_category ) %>%
		append_data( base_map, 
					., 
					key.shp="LGA_CODE11", 
					key.data="lga" 
					) -> df
		
		df %>%
		tm_shape( ) + 
		tm_polygons( "usage_level", 
					title = paste("Number of", name, "users in this LGA")
					) +
		tm_layout(frame=FALSE,
				legend.position = c("right", "top"), bg.color="lightgreen",
				inner.margins = c(.25,.02,.02,.25)) %>%
		{.} -> map
#
#
	df %>%
		tm_shape( xlim=get_state_capital_xlim(2),
				 ylim=get_state_capital_ylim(2) ) +
		tm_polygons( "usage_level", legend.show=FALSE) +
		tm_layout(frame=FALSE, bg.color="lightgreen")  %>%
		{.} -> m_melbourne

	df %>% 
		tm_shape( xlim=get_state_capital_xlim(1),
				ylim=get_state_capital_ylim(1) ) +
			tm_polygons( "usage_level", legend.show=FALSE) +
			tm_layout(frame=FALSE, bg.color="lightgreen")  %>%
		{.} -> m_sydney

	print(map)	
	# print insets
	print(m_sydney, vp=viewport(x= .6, y= .4, width= 0.2, height= 0.2))
	print(m_melbourne, vp=viewport(x= 0.27, y= 0.15, width= 0.2, height= 0.2))
}

#print_map_set( 3, 'long-term')
#print_map_set( 4, 'regular')


```
```{r play_with_maps}

#
df_patient_dose %>%
  group_by(pin, supply_year) %>%
  summarise(n_dose = sum( n_dose ) ) %>%
  inner_join( df_patient, by=c('pin')) %>%
	inner_join( df_patient_usage, by=c("pin")) %>%
	filter(is_geographic_LGA(lga)) %>%			
	select_and_standardise_ddd( standardise_over=qw( "lga" ), join_with="usage_category" ) %>%
	group_by( usage_category ) %>%
	mutate( usage_level = cut( ddd, 4, 
							  qw("low medium high very_high"), 
							  ordered=TRUE )) %>%
	ungroup() %>%
	{.} -> df_lga_summary

target_category=1
name='ads'
  
  #
print_map_ddd = function( target_category, name ) {

	df_lga_summary %>% 
		filter( as.integer(usage_category)==target_category ) %>%
		append_data( base_map, 
					., 
					key.shp="LGA_CODE11", 
					key.data="lga" 
					) %>%
		{.} -> df

	df %>%
		tm_shape( ) + 
		tm_polygons( "ddd", 
					title = paste("DDD of ", name, "users ")
					) +
		tm_layout(frame=FALSE,
				legend.position = c("right", "top"), bg.color="lightgreen",
				inner.margins = c(.25,.02,.02,.25)) %>%
		{.} -> map

	df %>%
			tm_shape( xlim=get_state_capital_xlim(2),
					ylim=get_state_capital_ylim(2) ) +
		tm_polygons( "ddd", legend.show=FALSE) +
		tm_layout(frame=FALSE, bg.color="lightgreen")  %>%
		{.} -> m_melbourne

	df %>% 
		tm_shape( xlim=get_state_capital_xlim(1),
				ylim=get_state_capital_ylim(1) ) +
		tm_polygons( "ddd", legend.show=FALSE) +
		tm_layout(frame=FALSE, bg.color="lightgreen")  %>%
		{.} -> m_sydney

	print(map)	
	# print insets
	print(m_sydney, vp=viewport(x= .55, y= .5, width= 0.2, height= 0.2))
	print(m_melbourne, vp=viewport(x= 0.27, y= 0.15, width= 0.2, height= 0.2))
	ggsave( paste0('/tmp/', name, '.png'))
}
name='One off'
print_map_ddd ( 4, 'Regular')
print_map_ddd ( 3, 'Long term')
print_map_ddd ( 2, 'Short term')
print_map_ddd ( 1, 'One off')

```





