---
title: "Hypothesis 3"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-04-30"
output: 
  word_document:
    reference_docx: ../../common/word_reference_style.docx
  html_document:
    code_folding: hide
---


```{r set-options, echo=FALSE, cache=FALSE, warning=FALSE, results='hide'}
rm(list=ls())
options(width = 200)
show_code = FALSE
source("lib/functions.R")
source("lib/standardisation.R")
source("lib/get_data.R")
source("lib/generate_data_frames.R")
```
#Methods

```{r data_preparation, echo=FALSE, cache=FALSE, results="hide", warning=FALSE}

data.cache( generate_data_frames, frequency='yearly')

```

# Methods
Patients who were dispensed at least in 15 quarters were identified as regular users.
Patients who were dispensed at least in 9 quarters were identified as long-term users.
Patients who were dispensed 1-8 quarters were identified as short-term users.
Patients who were dispensed just one occasion only were identified as one off users.

# plan
# find total doses and therefore ddd for each subgroup and LGA ( usage_category )
1) total doses for each subgroup, year, and lga (and age and sex )
2) normalise doses for each subgroup, based on age and sex for entire country
2a) take n_doses, divide by ratio for lga, and multiply by the ratio for the country
3) total normalised doses for entire lga
4) find ddd based on entire population for this lga and days_in_year (person_days)


```{r ppt_1, echo=FALSE}




read.dta13('data/Australian_population_for_merging.dta') %>%
  rename( age = age4, 
         sex = sex2,
         population = AusPop ) %>%
  as.tibble() %>% 
  { . } -> df_auspop

get_population_df() %>%
  group_by( age, sex, supply_year ) %>%
  summarise( population = sum( population ) )

#todo
df_patient_dose %>%
  inner_join( df_patient_usage ) %>%
  inner_join( df_patient ) %>%
  ungroup() %>%
  select_and_standardise_ddd(standardise_over=qw('lga usage_category'), 
                             join_with= c('supply_year'), 
                             f_join_population
                             ) %>% 
                             { . } -> df_lga_usage_ddd  

df_lga_usage_ddd %>%
  group_by( supply_year, usage_category ) %>%
  mutate( ddd_group = cut( ddd, 
                          quantile(ddd, probs= c(0, 0.25, 0.5, 0.75, 1) ), 
                          labels=as.character(1:4), 
                          include.lowest=TRUE) ) %>%
  ungroup() %>%
  { . } ->  lga_ddd_cut

write.csv( lga_ddd_cut,  'data/lgas_year_type_ddd.csv')

df_patient_dose %>%
	inner_join( df_patient_usage ) %>%
	inner_join( df_patient ) %>%
    select_and_standardise_ddd(standardise_over=qw('age usage_category'), 
                               join_with= c('supply_year'), 
                               f_join_population
                               ) %>% 
	mutate( year_age  = paste( age,supply_year) ) %>%
	select( -supply_year, -age ) %>%
	mutate( ddd=round(ddd,2)) %>%
	spread( year_age, ddd ) %>%
	write.csv('data/year_age_standardised.csv')


	df_patient_dose %>%
		inner_join( df_patient_usage ) %>%
		inner_join( df_patient ) %>%
        select_and_standardise_ddd(standardise_over=qw('state usage_category'), 
                                   join_with= c('supply_year'), 
                                   f_join_population
                                   ) %>% 
    	mutate( year_state  = paste( state, supply_year) ) %>%
		select( ddd, usage_category, year_state) %>%
		mutate( ddd=round(ddd,2)) %>%
		spread( year_state, ddd ) %>%
		write.csv('data/year_state_category_standardised.csv')


df %>% 
	mutate( state = ifelse( state=="VIC", "VIC", "NSW")) %>% 
	group_by( supply_year, state ) %>% 
	summarise( n_dose = sum(n_dose))  %>% 
	write.csv( 'data/doses.csv')

get_population_grouped(df_population, qw('state supply_year')) %>% 
	ungroup() %>%
	select(state, supply_year, population) %>%
	group_by( supply_year, state ) %>% 
	summarise( population = sum(population))  %>%
	write.csv('data/pop.csv')




shiny::runApp('explore/shiny/', display.mode = "normal")

target_category=4
name='asdf'

  #
print_map_ddd = function( target_category, name ) {

  lga_ddd_cut  %>%
    mutate( lga = as.factor( lga )) %>%
    filter( as.numeric(usage_category) ==target_category  & ddd_group == 4) %>%
    count( lga ) %>% 
    complete( lga, fill = list(n=0))  %>%
    mutate( lga=as.character(lga)) %>% 
    rbind( data.frame( lga=c(11860, 89399), n=0)) %>%
    mutate( n=as.ordered(n)) %>% 
      append_data( base_map, 
                  ., 
                  key.shp="LGA_CODE11", 
                  key.data="lga" 
                  )  %>%
      {.} -> df

    df %>%
      tm_shape( ) + 
      tm_polygons( "n", 
                  title = paste("Years", name, "users in highest quartile DDD ")
                  ) +
      tm_layout(frame=FALSE,
                legend.position = c("right", "top"), bg.color="lightgreen",
                inner.margins = c(.25,.02,.02,.25)) %>%
      {.} -> map

    df %>%
      tm_shape( xlim=get_state_capital_xlim(2),
               ylim=get_state_capital_ylim(2) ) +
      tm_polygons( "n", legend.show=FALSE) +
      tm_layout(frame=FALSE, bg.color="lightgreen")  %>%
      {.} -> m_melbourne

    df %>% 
      tm_shape( xlim=get_state_capital_xlim(1),
               ylim=get_state_capital_ylim(1) ) +
      tm_polygons( "n", legend.show=FALSE) +
      tm_layout(frame=FALSE, bg.color="lightgreen")  %>%
      {.} -> m_sydney

    print(map)	
    # print insets
    print(m_sydney, vp=viewport(x= .55, y= .5, width= 0.2, height= 0.2))
    print(m_melbourne, vp=viewport(x= 0.27, y= 0.15, width= 0.2, height= 0.2))
    save_tmap( map, paste0('/tmp/', name, '.png') )
}
  name='One off'
  print_map_ddd ( 4, 'regular')
  print_map_ddd ( 3, 'long term')
  print_map_ddd ( 2, 'Short term')
  print_map_ddd ( 1, 'One off')

```

