---
title: "Hypothesis 1"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2018-04-30"
output: 
  word_document:
    reference_docx: ../../common/word_reference_style.docx
---


```{r set-options, echo=FALSE, cache=FALSE, warning=FALSE, results='hide'}
rm(list=ls())
options(width = 200)
show_code = FALSE
setwd("~/mydoc/research/mofi/continuing/R")
source("functions.R")
source("get_data.R")
source("generate_data_frames.R")
```
#Methods

```{r data_preparation, echo=FALSE, cache=FALSE, results="hide", warning=FALSE}

data.cache( generate_data_frames, frequency='yearly')

```

# Methods
Patients who were dispensed at least in 15 quarters were identified as regular users.
Patients who were dispensed at least in 9 quarters were identified as long-term users.
Patients who were dispensed 1-8 quarters were identified as short-term users.
Patients who were dispensed just one occasion only were identified as one off users.

#powerpoint slide 1
```{r ppt_1, echo=FALSE}


df_patient_dose %>%
	inner_join( df_patient_usage ) %>%
	inner_join( df_patient ) %>%
	select( pin, usage_category, supply_year, age, sex, n_dose) %>% 
	select_and_standardise_ddd( standardise_over=qw( "age supply_year usage_category" )) %>%
	mutate( year_age  = paste( age,supply_year) ) %>%
	select( -supply_year, -age ) %>%
	mutate( ddd=round(ddd,2)) %>%
	spread( year_age, ddd ) %>%
	write.csv('/tmp/year_age_standardised.csv')

	kable() %>% clipr::write_clip()


	df_patient_dose %>%
		inner_join( df_patient_usage ) %>%
		inner_join( df_patient ) %>%
		group_by( state, usage_category, supply_year) %>% 
		summarise( n_dose = sum( n_dose ) )  %>%
		join_population_grouped( qw("state supply_year")) %>% 
		ungroup() %>%
		mutate( ddd = (n_dose * 1000 * 10) / (person_days)) %>% 
		mutate( year_state  = paste( state, supply_year) ) %>%
		select( ddd, usage_category, year_state) %>%
		mutate( ddd=round(ddd,2)) %>%
		spread( year_state, ddd ) %>%
		write.csv('/tmp/year_state_category_standardised.csv')

		ungroup() %>%
		print()


df %>% 
	mutate( state = ifelse( state=="VIC", "VIC", "NSW")) %>% 
	group_by( supply_year, state ) %>% 
	summarise( n_dose = sum(n_dose))  %>% 
	write.csv( '/tmp/doses.csv')

get_population_grouped(qw('state supply_year')) %>% 
	ungroup() %>%
	select(state, supply_year, population) %>%
	mutate( state = ifelse( state=="VIC", "VIC", "NSW")) %>% 
	group_by( supply_year, state ) %>% 
	summarise( population = sum(population))  %>%
	write.csv('/tmp/pop.csv')



